---
title: "Portfolio 7"
---
Goal: The goal of this portfolio piece was to create a figure for my thesis that illustrated an insignificant relationship between two variables. 
```{r load-packages, echo=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(stats)
library(psych)
library(tidyr)
library(haven)
library(ggplot2)
```
```{r import-data, echo=FALSE, message=FALSE, warning=FALSE}
pulse_data <- read_sav("/Users/tiffani/Downloads/PULSE_combined.sav")

pulse_data <- pulse_data %>%
  mutate(
    comp_intention = rowMeans(
      select(., likely_2_6, likely_3_8),
      na.rm = TRUE
    )
  )
```
```{r summarize-data, echo=FALSE, message=FALSE}
summary_pulse <- pulse_data %>% 
  group_by(condition) %>% 
  summarise(
    mean = mean(comp_intention, na.rm = TRUE),
    sd = sd(comp_intention, na.rm = TRUE),
    n = n(),
    se = sd/sqrt(n)
  )
```

This graphic does a pretty good job of actually depicting what is goig on with the data. I think there may be some room for improvement, but I also want to see how this looks with just points.


```{r plot-data, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summary_pulse, aes(x = condition, y = mean)) +
  geom_col(fill = "pink", width = 0.5) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
  labs(x = "Condition", y = "Intention to Enroll") +

   scale_x_discrete(labels= c(
    diversity = "Intervention",
    p_involvement = "Control"
  )) +
  theme_minimal()
```

I think this exacerbates the actual gap between the two conditions. There's wasn't much of a difference between the two, but this shows otherwise.

```{r plot-data-2, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summary_pulse, aes(x = condition, y = mean)) +
  geom_point(fill = "pink", size = 3) +
  geom_line() +
  
  labs(x = "Condition", y = "Intention to Enroll") +
   scale_x_discrete(labels= c(
    diversity = "Intervention",
    p_involvement = "Control"
  )) +
  theme_minimal()
```
