---
title: "Portfolio 8"
---
Goal: The goal of this portfolio was to create a figures visualizing the correlations between two dependent measures used in my thesis. The two variables I choose were "prioritization of diverse schools" and "diverse-school enrollment efficacy". 
```{r load-packages, message =FALSE, echo = FALSE}
library(readr)
library(dplyr)
library(stats)
library(psych)
library(tidyr)
library(haven)
library(lavaan)
library(ggplot2)

pulse_data <- read_sav("/Users/tiffani/Downloads/PULSE_combined.sav")
```
```{r plot, message=FALSE, echo=FALSE}
 
ggplot(pulse_data, aes(x = diverse_choice_sum, y = confident_diversity_comp2))+
  geom_point() +
  labs(x = "Diverse-school Enrollment Efficacy", y = "Prioritization of Diverse Schools")
```
The variables are discrete, so I think this is overplotted. Here's how I fixed that issue:


```{r plot-again, message=FALSE, echo=FALSE}

ggplot(pulse_data, aes(x = diverse_choice_sum, y = confident_diversity_comp2)) +
  geom_jitter(width = 0.2, height = 0.2) +
  labs(x = "Diverse-school Enrollment Efficacy", y = "Prioritization of Diverse Schools")

```

I'm not sure if I would call this the "perfect figure", but it is a lot more interpretable than the first one. We can see that priortization of diverse schools and diverse school enrollment efficacy was corrrelated.
```{r plot-again2, message=FALSE, echo=FALSE}
ggplot(pulse_data, aes(x = diverse_choice_sum, y = confident_diversity_comp2)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Diverse-school Enrollment Efficacy", y = "Prioritization of Diverse Schools")
```
